Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-26 paper.tex

%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado 
% And this is going to be useful because... - JJ

@@

\subsection{Results for all the editors}
\label{subsec:results_all_editors}

In the first stage of the experiments, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models. SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value. Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
% Antonio - Sam, verify this, please
% Sam - reviewed and fixed

@@

***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.

@@

***TODO***: Justify the selected features by SOM (why have we chosen them?).

@@

***TO DO***: comment the results

***TO DO***: Think if including the graphs (scatter plots).

@@

***TO DO ***: Justify the special cases (why we have chosen them).

>>>>

%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado 
% And this is going to be useful because... - JJ
% This is copied from the HIV paper. Please rephrase and adapt to the
% particular venue - JJ

@@

\subsection{Results for all editors}
\label{subsec:results_all_editors}

In the first stage of the experiments, forecasting methods have been
applied to the whole dataset. All the pre-sales features have been
considered, including the categorical ones, which make it harder to
process the instances and build the different models. SVM for
instance, must previously transform these categories into binary
variables in order to deal with the data, which means the creation of
a different (and new) variable per each possible value. Thus, in the
case of editorial or collection this would imply the definition of
hundreds of new variables.

@@

%***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.

@@

%***TODO***: Justify the selected features by SOM (why have we chosen them?).

@@

%***TO DO***: comment the results

%***TO DO***: Think if including the graphs (scatter plots).

@@

%***TO DO ***: Justify the special cases (why we have chosen them).
